% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{David Pierson Bradway, Ph.D.}
\author{}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={David Pierson Bradway, Ph.D.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage[vmargin=1in,hmargin=1in]{geometry}

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

\href{mailto:david.bradway@duke.edu}{\nolinkurl{david.bradway@duke.edu}}\\
Research Scientist, Biomedical Engineering\\
Duke University, Durham, NC 27708 USA

\hypertarget{objective}{%
\subsection{Objective}\label{objective}}

\begin{itemize}
\tightlist
\item
  Use technical and administrative skills to facilitate projects
  advancing state of the art imaging techniques
\item
  Utilize knowledge of data science, visualization, imaging, and
  research operations at Duke
\item
  Further refine skills in project and program management, science and
  engineering, and research and development
\end{itemize}

\hypertarget{work-experience}{%
\subsection{Work Experience}\label{work-experience}}

\begin{itemize}
\item
  \textbf{Duke University} (Durham, NC, USA)

  Research Scientist, Laboratory of Gregg Trahey, 2014 - present

  \begin{itemize}
  \tightlist
  \item
    Clincal research coordination for studies on ultrsound imaging in
    the engineering lab, as well as hospital fetal and liver clinics
  \item
    Collaborate with industry and academic partners and Duke graduate
    students on NIH grants
  \item
    Developing technical tools, managing data and documentation for the
    lab group
  \end{itemize}
\item
  \textbf{Technical University of Denmark (DTU)} (Kongens Lyngby,
  Denmark)

  Postdoctoral Researcher, Laborartory of Jørgen Jensen, 2013 - 2014

  \begin{itemize}
  \tightlist
  \item
    Wrote OpenCL code to process 3-D vector flow imaging data on an AMD
    GPU
  \item
    Presented a conference presentation, a poster, and proceedings (SPIE
    2014 \& 2015)
  \item
    Contributed as co-author to another peer-reviewed journal article
  \item
    Examined feasibility of transthoracic cardiac vector flow imaging on
    a phased-array probe
  \end{itemize}
\item
  \textbf{Duke University} (Durham, NC, USA)

  Graduate Research and Teaching Assistant, 2005 - 2013

  \begin{itemize}
  \tightlist
  \item
    PhD project using ultrasound to noninvasively measure the heart's
    mechanical properties
  \item
    Organized and conducted clinical studies at Duke University Medical
    Center
  \item
    Presented results in conferences and proceedings and via
    peer-reviewed journal articles
  \item
    Graduate-level medical imaging coursework and labs covering CT, MR,
    OCT and nuclear imaging
  \end{itemize}
\item
  \textbf{Siemens Healthcare} (Issaquah, WA, USA)

  Graduate Student Research Intern, 2008

  \begin{itemize}
  \tightlist
  \item
    Worked within a research and development team in a large corporation
  \item
    Added multiple focal zone ARFI excitation to research mode of Acuson
    S2000 ultrasound scanner
  \item
    Learned
    \href{http://www-03.ibm.com/software/products/en/clearcase}{version
    control} and \href{http://www.visualstudio.com/}{MS Visual Studio
    IDE} tools
  \end{itemize}
\end{itemize}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{itemize}
\item
  \textbf{Duke University} (Durham, NC, USA)

  \href{http://bme.duke.edu/grad}{Ph.D.~in Biomedical Engineering}, May
  2013.
\item
  \textbf{The Ohio State University (OSU)} (Columbus, OH, USA)

  \href{http://ece.osu.edu/futurestudents/undergrad}{B.S. in Electrical
  and Computer Engineering}, June 2005.
\end{itemize}

\hypertarget{teaching}{%
\subsection{Teaching}\label{teaching}}

\begin{itemize}
\tightlist
\item
  Co-Instructor, Instructor, Adv. Top. Lab for Grads in BME - Intro. to
  Electronics Biomedical Engineering 790L (2018, 2019)
\item
  Instructor, Ultrasound module of Medical Physics 731 (2015, 2016)
\item
  Guest lecturer, Biomedical Engineering 590 (2016)
\item
  Co-Instructor,~International Summer School on Advanced Ultrasound
  Imaging, Technical University of Denmark (2015)
\end{itemize}

\hypertarget{grants-and-contracts}{%
\subsection{Grants and Contracts}\label{grants-and-contracts}}

\begin{itemize}
\tightlist
\item
  \href{https://dibs.duke.edu/research/awards/schedule-application}{2019
  Research Germinator Award, Duke Institute for Brain Sciences (DIBS)}
  Ravikanth Velagapudi, PhD, Anesthesiology, School of Medicine; and
  William Huffman and David Bradway, PhD, Biomedical Engineering, Pratt
  School of Engineering. Targeting Autophagy with Non-Invasive Vagal
  Nerve Stimulation to Treat Delirium Superimposed on Dementia.
\end{itemize}

\hypertarget{invention-disclosures-and-patents}{%
\subsection{Invention Disclosures and
Patents}\label{invention-disclosures-and-patents}}

\begin{itemize}
\tightlist
\item
  Duke IDF \#a3348ed7: ``Split Aperture ARFI / SWEI''
\item
  Duke IDF \#540: ``Visual Feedback for Improved Triggered Acquisitions
  for Ultrasound Imaging''
\item
  Trahey, G., Long, W., Hollender, P., Bradway, D., Kakkad, V. and
  Bottenus, N., Duke University, 2021. Methods, systems and computer
  program products for triggering ultrasound data acquisition. U.S.
  Patent 10,969,487.
\end{itemize}

\hypertarget{honors-and-activities}{%
\subsection{Honors and Activities}\label{honors-and-activities}}

\begin{itemize}
\tightlist
\item
  \href{http://www.whitaker.org/grants/fellows-scholars}{Whitaker
  International Program Scholar} (2013)
\item
  \href{http://www.nsfgrfp.org/}{National Science Foundation Graduate
  Research Fellow} (2005-2008)
\item
  \href{https://goldwater.scholarsapply.org/}{Goldwater Research
  Scholar} (2004-2005)
\item
  \href{http://www.montanadeluz.org/}{Organized engineering design and
  build trip to Honduran orphanage} (2004)
\item
  \href{http://ecos.osu.edu/}{Founded engineering community service
  group at Ohio State} (2003)
\end{itemize}

\hypertarget{professional-activities}{%
\subsection{Professional Activities}\label{professional-activities}}

\begin{itemize}
\tightlist
\item
  Early Career Professional Development in Medical Imaging Workshop,
  SPIE Medical Imaging (2015)
\item
  Associate Editor, Ultrasonic Imaging journal (2016-)
\item
  Reviewer for the journals Ultrasound in Medicine and Biology,
  Ultrasonic Imaging, and IEEE Transactions on Medical Imaging, Journal
  of Medical Imaging
\item
  Duke Machine Learning Summer School (2019)
\item
  Hands-On Deep Learning for Processing of Biosignals Short Course.
  ASSIST Center, North Carolina State University (2021)
\end{itemize}

\hypertarget{skills}{%
\subsection{Skills}\label{skills}}

\begin{itemize}
\tightlist
\item
  Advanced signal and imaging processing programming: Matlab and Python
\item
  Tools and languages: \href{http://git-scm.com/}{Git}, C/C++,
  OpenCL/CUDA, Docker, Linux
\item
  Problem solving, signal and image analysis, data science, scientific
  computing, and experimental design
\item
  Strong written and verbal communication, data visualization
\item
  Successfully written fellowships, scholarships, proposals
\item
  Personal hardware and software projects in embedded systems:
  \href{http://www.arduino.cc/}{Arduino},
  \href{http://www.raspberrypi.org/}{Raspberry Pi}
\end{itemize}

\hypertarget{journal-articles}{%
\subsubsection{Journal Articles}\label{journal-articles}}

{[}1--13{]}

\hypertarget{book-chapters}{%
\subsubsection{Book Chapters}\label{book-chapters}}

{[}14,15{]}

\hypertarget{abstracts-and-proceedings}{%
\subsubsection{Abstracts and
Proceedings}\label{abstracts-and-proceedings}}

{[}16--47{]}

\hypertarget{publications}{%
\subsection*{Publications}\label{publications}}
\addcontentsline{toc}{subsection}{Publications}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Fahey2008a}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{Fahey BJ, Nelson RC, Bradway DP, Hsu SJ, Dumont DM, et
al. (2008) {In vivo visualization of abdominal malignancies with
acoustic radiation force elastography}. Physics in medicine and biology
53: 279--93.
doi:\href{https://doi.org/10.1088/0031-9155/53/1/020}{10.1088/0031-9155/53/1/020}}

\leavevmode\vadjust pre{\hypertarget{ref-Fahey2008c}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{Fahey BJ, Nelson RC, Hsu SJ, Bradway DP, Dumont DM, et
al. (2008) {In vivo guidance and assessment of liver radio-frequency
ablation with acoustic radiation force elastography}. Ultrasound in
medicine \& biology 34: 1590--603.
doi:\href{https://doi.org/10.1016/j.ultrasmedbio.2008.03.006}{10.1016/j.ultrasmedbio.2008.03.006}}

\leavevmode\vadjust pre{\hypertarget{ref-Nightingale2008}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{Nightingale K, Palmeri M, Zhai L, Frinkley K, Wang M, et
al. (KR) {Impulsive acoustic radiation force: imaging approaches and
clinical applications}. The Journal of the Acoustical Society of America
123: 3792.
doi:\href{https://doi.org/10.1121/1.2935460}{10.1121/1.2935460}}

\leavevmode\vadjust pre{\hypertarget{ref-Nightingale2009}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{Nightingale K, Palmeri M, Dahl J, Bradway D, Hsu S, et
al. (2009) Elasticity imaging with acoustic radiation force: Methods and
clinical applications. Japanese journal of medical ultrasonics 36: 116.}

\leavevmode\vadjust pre{\hypertarget{ref-Wolf2011}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{Wolf PD, Eyerly SA, Bradway DP, Dumont DM, Bahnson TD,
et al. (2011) {Near real time evaluation of cardiac radiofrequency
ablation lesions with intracardiac echocardiography based acoustic
radiation force impulse imaging}. The Journal of the Acoustical Society
of America 129: 2438.
doi:\href{https://doi.org/10.1121/1.3587978}{10.1121/1.3587978}}

\leavevmode\vadjust pre{\hypertarget{ref-Eyerly2012}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{Eyerly SA, Bahnson TD, Koontz JI, Bradway DP, Dumont DM,
et al. (2012) {Intracardiac acoustic radiation force impulse imaging: A
novel imaging method for intraprocedural evaluation of radiofrequency
ablation lesions}. Heart rhythm: the official journal of the Heart
Rhythm Society 9: 1855--1862.
doi:\href{https://doi.org/10.1016/j.hrthm.2012.07.003}{10.1016/j.hrthm.2012.07.003}}

\leavevmode\vadjust pre{\hypertarget{ref-Hollender2013}{}}%
\CSLLeftMargin{7. }
\CSLRightInline{Hollender P, Bradway D, Wolf P, Goswami R, Trahey G
(2013) Intracardiac acoustic radiation force impulse (ARFI) and shear
wave imaging in pigs with focal infarctions. IEEE transactions on
ultrasonics, ferroelectrics, and frequency control 60: 1669--1682.
doi:\href{https://doi.org/10.1109/TUFFC.2013.2749}{10.1109/TUFFC.2013.2749}}

\leavevmode\vadjust pre{\hypertarget{ref-Patel2014}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Patel V, Dahl JJ, Bradway DP, Doherty JR, Lee SY, et al.
(2014) {Acoustic Radiation Force Impulse Imaging (ARFI) on an IVUS
Circular Array}. Ultrasonic Imaging 36: 98--111.
doi:\href{https://doi.org/10.1177/0161734613511595}{10.1177/0161734613511595}}

\leavevmode\vadjust pre{\hypertarget{ref-Eyerly2014}{}}%
\CSLLeftMargin{9. }
\CSLRightInline{Eyerly SA, Bahnson TD, Koontz JI, Bradway DP, Dumont DM,
et al. (2014) {Contrast in Intracardiac Acoustic Radiation Force Impulse
Images of Radiofrequency Ablation Lesions}. Ultrasonic Imaging 36:
133--148.
doi:\href{https://doi.org/10.1177/0161734613519602}{10.1177/0161734613519602}}

\leavevmode\vadjust pre{\hypertarget{ref-jensen2016}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{Jensen JA, Rasmussen MF, Pihl MJ, Holbek S, Villagómez
HCA, et al. (2016) Safety assessment of advanced imaging sequences i:
measurements. IEEE transactions on ultrasonics, ferroelectrics, and
frequency control 63: 110--119.
doi:\href{https://doi.org/10.1109/TUFFC.2015.2502987}{10.1109/TUFFC.2015.2502987}}

\leavevmode\vadjust pre{\hypertarget{ref-bottenus2016}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{Bottenus N, Long W, Zhang H, Jakovljevic M, Bradway D,
et al. (2016) Feasibility of swept synthetic aperture ultrasound
imaging.
doi:\href{https://doi.org/10.1109/TMI.2016.2524992}{10.1109/TMI.2016.2524992}}

\leavevmode\vadjust pre{\hypertarget{ref-Long2017umb}{}}%
\CSLLeftMargin{12. }
\CSLRightInline{Long W, Hyun D, Roy Choudhury K, Bradway D, McNally P,
et al. (2018) {Clinical utility of fetal short-lag spatial coherence
imaging}. Ultrasound in Medicine and Biology 44: 794--806.
doi:\href{https://doi.org/10.1016/j.ultrasmedbio.2017.12.006}{10.1016/j.ultrasmedbio.2017.12.006}}

\leavevmode\vadjust pre{\hypertarget{ref-Flint2020}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{Flint K, Bottenus N, Bradway D, McNally P, Ellestad S,
et al. (2021) {An Automated ALARA Method for Ultrasound: An Obstetric
Ultrasound Feasibility Study}. Journal of Ultrasound in Medicine 40:
1863--1877. Available:
\url{https://onlinelibrary.wiley.com/doi/abs/10.1002/jum.15570}.}

\leavevmode\vadjust pre{\hypertarget{ref-dobbins2019medical}{}}%
\CSLLeftMargin{14. }
\CSLRightInline{Dobbins JT, Frush DP, Kigongo CJ, MacFall JR, Reiman RE,
et al. (2019) Medical imaging safety in global health radiology.
Radiology in global health. Springer. pp. 85--105.}

\leavevmode\vadjust pre{\hypertarget{ref-eyerly2018acoustic}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{Eyerly-Webb SA, Vejdani-Jahromi M, Kakkad V, Hollender
P, Bradway D, et al. (2018) Acoustic radiation force-based ultrasound
elastography for cardiac imaging applications. Ultrasound elastography
for biomedical applications and medicine. John Wiley \& Sons. pp.
504--519.}

\leavevmode\vadjust pre{\hypertarget{ref-Hsu2007c}{}}%
\CSLLeftMargin{16. }
\CSLRightInline{Hsu SJ, Bradway DP, Fahey BJ, Trahey GE (2007)
{Transthoracic Acoustic Radiation Force Impulse Imaging of the Cardiac
Cycle}. Ultrasonic measurement and imaging of tissue elasticity.}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2007}{}}%
\CSLLeftMargin{17. }
\CSLRightInline{Bradway DP, Hsu SJ, Fahey BJ, Dahl JJ, Nichols TC, et
al. (2007) {6B-6 Transthoracic Cardiac Acoustic Radiation Force Impulse
Imaging: A Feasibility Study}. IEEE. pp. 448--451.
doi:\href{https://doi.org/10.1109/ULTSYM.2007.121}{10.1109/ULTSYM.2007.121}}

\leavevmode\vadjust pre{\hypertarget{ref-Fahey2007b}{}}%
\CSLLeftMargin{18. }
\CSLRightInline{Fahey BJ, Nelson RC, Hsu SJ, Bradway DP, Dumont DM, et
al. (2007) {6B-4 In Vivo Acoustic Radiation Force Impulse Imaging of
Abdominal Lesions}. 2007 IEEE ultrasonics symposium proceedings. IEEE.
pp. 440--443.
doi:\href{https://doi.org/10.1109/ULTSYM.2007.119}{10.1109/ULTSYM.2007.119}}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2009}{}}%
\CSLLeftMargin{19. }
\CSLRightInline{Bradway DP, Fahey BJ, Nelson RC, Trahey GE (2009) {ARFI
imaging of abdominal ablation and liver lesion biopsy}. International
symposium on ultrasonic imaging and tissue characterization, 2009.
Available: \url{http://uitc-symposium.org/2009_abstracts.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Husarik2009}{}}%
\CSLLeftMargin{20. }
\CSLRightInline{Husarik DB, Nelson RC, Bradway DP, Fahey BJ, Nightingale
KR, et al. (2009) {First Clinical Experience with Sonographic
Elastography of the Liver Using Acoustic Radiation Force Impulse (ARFI)
Imaging}. RSNA. Available: \url{http://rsna2009.rsna.org/search}.}

\leavevmode\vadjust pre{\hypertarget{ref-Nelson2009}{}}%
\CSLLeftMargin{21. }
\CSLRightInline{Nelson RC, Bradway DP, Fahey BJ, Trahey GE (2009)
{Future Application of Ultrasound: Acoustic Radiation Force Impulse
(ARFI) Imaging}. AIUM. Available:
\url{http://www.aium.org/loginRequired/membersOnly/proceedings/2009.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2009b}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{Bradway DP, Fahey BJ, Nelson RC, Trahey GE (2009)
{Recent Clinical Results of Acoustic Radiation Force Impulse Imaging of
Abdominal Ablation}. International tissue elasticity conference.
Available:
\url{http://www.elasticityconference.org/prior_conf/2009/PDF/2009Proceedings.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Hsu2010}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Hsu SJ, Bradway DP, Bouchard RR, Hollender PJ, Wolf PD,
et al. (2010) {Parametric pressure-volume analysis and acoustic
radiation force impulse imaging of left ventricular function}. 2010 IEEE
international ultrasonics symposium. IEEE. pp. 698--701.
doi:\href{https://doi.org/10.1109/ULTSYM.2010.5935661}{10.1109/ULTSYM.2010.5935661}}

\leavevmode\vadjust pre{\hypertarget{ref-Hollender2010}{}}%
\CSLLeftMargin{24. }
\CSLRightInline{Hollender PJ, Bouchard RR, Hsu SJ, Bradway DP, Wolf PD,
et al. (2010) {Intracardiac measurements of elasticity using Acoustic
Radiation Force Impulse (ARFI) methods: Temporal and spatial stability
of shear wave velocimetry}. 2010 IEEE international ultrasonics
symposium. IEEE. pp. 698--701.
doi:\href{https://doi.org/10.1109/ULTSYM.2010.5935946}{10.1109/ULTSYM.2010.5935946}}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2010}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{Bradway DP, Hsu SJ, Wolf PD, Trahey GE (2010) {Acoustic
Radiation Force Impulse Imaging of Acute Myocardial Ischemia and
Infarct}. International symposium on ultrasonic imaging and tissue
characterization. Available:
\url{http://uitc-symposium.org/2010_abstracts.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2010b}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Bradway DP, Hsu SJ, Wolf PD, Trahey GE (2010)
{Transthoracic Acoustic Radiation Force Impulse Imaging of Cardiac
Function}. International tissue elasticity conference. Available:
\url{http://www.elasticityconference.org/prior_conf/2010/PDF/2010Proceedings.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2011}{}}%
\CSLLeftMargin{27. }
\CSLRightInline{Bradway DP, Rosenzweig SR, Doherty JR, Hyun D, Trahey GE
(2011) {Recent Results and Advances in Transthoracic Cardiac Acoustic
Radiation Force Impulse Imaging}. International symposium on ultrasonic
imaging and tissue characterization. Available:
\url{http://www.elasticityconference.org/prior_conf/2011/PDF/2011ITECProceedings.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Byram2011}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{Byram BC, Gianantonio DM, Bradway DP, Hyun D,
Jakovljevic M, et al. (2011) {Direct in vivo Myocardial Infarct
Visualization Using 3D Ultrasound and Passive Strain Contrast}.
International tissue elasticity conference. Available:
\url{http://www.elasticityconference.org/prior_conf/2011/PDF/2011ITECProceedings.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Byram2011b}{}}%
\CSLLeftMargin{29. }
\CSLRightInline{Byram BC, Bradway DP, Jakovljevic M, Gianantonio D, Hyun
D, et al. (2011) {Direct In Vivo Myocardial Infarct Visualization Using
3D Ultrasound and Passive Strain Contrast}. IEEE ultrasonics symp.
doi:\href{https://doi.org/10.1109/ULTSYM.2011.0007}{10.1109/ULTSYM.2011.0007}}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2012}{}}%
\CSLLeftMargin{30. }
\CSLRightInline{Bradway DP, Hollender PJ, Goswami R, Wolf PD, Trahey GE
(2012) Feasibility and safety of transthoracic cardiac acoustic
radiation force impulse imaging methods. 2012 IEEE international
ultrasonics symposium. IEEE. pp. 2027--2030.
doi:\href{https://doi.org/10.1109/ULTSYM.2012.0507}{10.1109/ULTSYM.2012.0507}}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2012b}{}}%
\CSLLeftMargin{31. }
\CSLRightInline{Bradway DP, Hollender PJ, Goswami R, Wolf PD, Trahey GE
(2012) {Transthoracic Cardiac Acoustic Radiation Force Impulse Imaging:
in vivo Feasibility, Methods, and Initial Results}. International
symposium on ultrasonic imaging and tissue characterization, 2012.
Available: \url{http://uitc-symposium.org/2012_abstracts.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Hollender2012}{}}%
\CSLLeftMargin{32. }
\CSLRightInline{Hollender PJ, Bradway DP, Goswami R, Wolf PD, Trahey GE
(2012) {Acoustic radiation force techniques for imaging cardiac infarct
in vivo: methods and initial results}. International symposium on
ultrasonic imaging and tissue characterization. Available:
\url{http://uitc-symposium.org/2012_abstracts.pdf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Eyerly2012b}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{Eyerly SA, Bahnson T, Koontz J, Bradway DP, Dumont DM,
et al. (2012) {Confirmation of Cardiac Radiofrequency Ablation Treatment
Using Intra-Procedure Acoustic Radiation Force Impulse Imaging}. IEEE
ultrasonics symposium.
doi:\href{https://doi.org/10.1109/ULTSYM.2012.0509}{10.1109/ULTSYM.2012.0509}}

\leavevmode\vadjust pre{\hypertarget{ref-Hollender2012b}{}}%
\CSLLeftMargin{34. }
\CSLRightInline{Hollender PJ, Bradway DP, Wolf PD, Goswami R, Trahey GE
(2012) {Intracardiac ARF-driven Shear Wave Velocimetry to Estimate
Regional Myocardial Stiffness and Contractility in Pigs with Focal
Infarctions}. IEEE ultrasonics symposium.
doi:\href{https://doi.org/10.1109/ULTSYM.2012.0508}{10.1109/ULTSYM.2012.0508}}

\leavevmode\vadjust pre{\hypertarget{ref-Goswami2013}{}}%
\CSLLeftMargin{35. }
\CSLRightInline{Goswami R, Bradway D, Kisslo J, Trahey G (2013) {Novel
Application of Acoustic Radiation Force Impulse Imaging in Transthoracic
Echocardiography}. Journal of the american college of cardiology.
American College of Cardiology Foundation, Vol. 61. p. E1090.
doi:\href{https://doi.org/10.1016/S0735-1097(13)61090-6}{10.1016/S0735-1097(13)61090-6}}

\leavevmode\vadjust pre{\hypertarget{ref-Patel2013}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{Patel V, Dahl JJ, Bradway DP, Doherty JR, Smith SW
(2013) {Acoustic radiation force impulse imaging on an IVUS circular
array}. 2013 IEEE international ultrasonics symposium (IUS). IEEE. pp.
773--776.
doi:\href{https://doi.org/10.1109/ULTSYM.2013.0199}{10.1109/ULTSYM.2013.0199}}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2014}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{Bradway DP, Pihl MJ, Krebs andreas, Tomov BG, Kjær CS,
et al. (2014) {Real-time GPU implementation of transverse oscillation
vector velocity flow imaging}. SPIE medical imaging.Vol. 9040. pp.
90401Y-90401Y-6.
doi:\href{https://doi.org/10.1117/12.2043582}{10.1117/12.2043582}}

\leavevmode\vadjust pre{\hypertarget{ref-Bradway2015}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{Bradway DP, Hansen KL, Nielsen MB, Jensen JA (2015)
{Transverse oscillation vector flow imaging for transthoracic
echocardiography}. SPIE medical imaging. pp. 941902-941902-7.
doi:\href{https://doi.org/10.1117/12.2081145}{10.1117/12.2081145}}

\leavevmode\vadjust pre{\hypertarget{ref-Bottenus2015}{}}%
\CSLLeftMargin{39. }
\CSLRightInline{Bottenus N, Long W, Bradway D, Trahey G (2015) Phantom
and in vivo demonstration of swept synthetic aperture imaging. 2015 IEEE
international ultrasonics symposium (IUS). pp. 1--4.
doi:\href{https://doi.org/10.1109/ULTSYM.2015.0075}{10.1109/ULTSYM.2015.0075}}

\leavevmode\vadjust pre{\hypertarget{ref-Kakkad2015}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{Kakkad V, Kuo L, Bradway D, Trahey G, Sivak J, et al.
(2015) In vivo transthoracic measurements of acoustic radiation force
induced displacements in the heart over the cardiac cycle. 2015 IEEE
international ultrasonics symposium (IUS). pp. 1--5.
doi:\href{https://doi.org/10.1109/ULTSYM.2015.0155}{10.1109/ULTSYM.2015.0155}}

\leavevmode\vadjust pre{\hypertarget{ref-Kakkad2017}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{Kakkad V, Ferlauto H, Bradway D, Heyde B, Kisslo J, et
al. (2017) {Clinical feasibility of a noninvasive method to interrogate
myocardial function via strain and acoustic radiation force-derived
stiffness}. IEEE international ultrasonics symposium, IUS.
doi:\href{https://doi.org/10.1109/ULTSYM.2017.8092067}{10.1109/ULTSYM.2017.8092067}}

\leavevmode\vadjust pre{\hypertarget{ref-Hollender2017}{}}%
\CSLLeftMargin{42. }
\CSLRightInline{Hollender P, Bottenus N, Bradway D, Trahey G (2017)
{Single track location comb-push ultrasound shear elastography
(STL-CUSE)}. IEEE international ultrasonics symposium, IUS.
doi:\href{https://doi.org/10.1109/ULTSYM.2017.8092809}{10.1109/ULTSYM.2017.8092809}}

\leavevmode\vadjust pre{\hypertarget{ref-Long2017IUS}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{Long W, Hyun D, Choudhury K, Bradway D, McNally P, et
al. (2017) Translation of fetal short-lag spatial coherence (SLSC)
imaging into clinical practice: A pilot study. 2017 IEEE international
ultrasonics symposium (IUS). pp. 1--1.
doi:\href{https://doi.org/10.1109/ULTSYM.2017.8091968}{10.1109/ULTSYM.2017.8091968}}

\leavevmode\vadjust pre{\hypertarget{ref-Flint2018}{}}%
\CSLLeftMargin{44. }
\CSLRightInline{Flint K, Bottenus N, Long W, Bradway D, McNally P, et
al. (2018) Implementation and clinical evaluation of a fetal ALARA
ultrasound system. 2018 IEEE international ultrasonics symposium (IUS).
pp. 1--4.
doi:\href{https://doi.org/10.1109/ULTSYM.2018.8579734}{10.1109/ULTSYM.2018.8579734}}

\leavevmode\vadjust pre{\hypertarget{ref-Bernard2018}{}}%
\CSLLeftMargin{45. }
\CSLRightInline{Bernard O, Bradway D, Hansen HHG, Kruizinga P, Nair A,
et al. (2018) {The Ultrasound File Format (UFF) - First Draft}. 2018
IEEE international ultrasonics symposium. IEEE.}

\leavevmode\vadjust pre{\hypertarget{ref-Hollender2019}{}}%
\CSLLeftMargin{46. }
\CSLRightInline{Hollender P, Noor S, Bradway D, Trahey G (2019)
{Force-Map Normalization for ARFI Imaging}. 2019 IEEE international
ultrasonics symposium. IEEE. pp. 411--414.}

\leavevmode\vadjust pre{\hypertarget{ref-Huber2021}{}}%
\CSLLeftMargin{47. }
\CSLRightInline{Huber M, Flint K, Barre E, Bradway D, McNally P, et al.
(2021) Mechanisms affecting ALARA MI selected in adaptive ultrasound
imaging. 2021 IEEE international ultrasonics symposium (IUS). pp. 1--4.
doi:\href{https://doi.org/10.1109/IUS52206.2021.9593860}{10.1109/IUS52206.2021.9593860}}

\end{CSLReferences}

\end{document}
